Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-05 doc/PRF2022/Supplementary.tex
supplementary material

\noindent 
Szu-Pei Fu$^{1,*},$ 
Rolf Ryham$^{2},$ 
Bryan Quaife$^{3},$ 
Y.-N. Young$^{4},$
\\

@@

\noindent
{\bf Movie S1. Relaxation} 
There are 60 circular particles with radius 1.25 nm that are initially confined in a square box.
The simulation results show the relaxation with the use of all three boundary conditions.
The color on the boundary from blue to red
is for $\min g(\xx)$ to $\max g(\xx)$.
All final configurations are adopted in 
simulations with hydrodynamic flows.
The time step of all simulations is $\Delta t=0.2$.\\

\noindent
{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the shear flow. 
For the choices of the shear rate, we pick: $\dot\gamma = 0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, 
$\dot\gamma = 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated configurations.
The vesicle case undergoes tank treading
whereas the initially disordered BC (i) case
increases orientational order.  The multilamellar
assemply behaves a rigid body,
and the striated configuration moreso.
There are no ruptures that occur in this movie.\\

\noindent
{\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow
at relatively low flow rates.
For the choices of the flow strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the
disordered bilayer, 
$V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$ for the striated configurations.
The vesicle stays inact, whereas the dissordered bilayer is pulled apart.
Like in Supplementary Movie S2, the striated assembly is basically rigid.\\

@@

\noindent
{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow
for high flow rates. 
In this movie, some clear structural ruptures occur in each case.
For the choices of the flow strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the bilayer, 
$V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the striated configurations.
In all cases, there is significant reduction in the orientational order of the assemblies.
While the BC (i) cases are broken into several pieces, the main body of the
BC (ii) and BC (iii) assemblies is not pulled apart by the background flow. 
\\

>>>>

\noindent 
Szu-Pei Fu$^{1,*},$ 
Rolf Ryham$^{2},$ 
Bryan Quaife$^{3}$ and Y.-N. Young$^{4},$
\\

@@

\noindent
{\bf Movie S1. Relaxation} 
There are 60 circular particles with radius 1.25~nm that are initially
confined in a square box. The simulation results show the relaxation
with each of the three boundary conditions. The time step of all
simulations is $\Delta t=0.2$. The color on the boundary from blue to
red is for $\min g(\xx)$ to $\max g(\xx)$. All final configurations are
adopted in simulations with hydrodynamic flows. \\

\noindent
{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, $\dot\gamma
= 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated
configurations. The vesicle case undergoes tank-treading whereas the
initially disordered BC (i) case increases orientational order. The
multilamellar assemply behaves as a rigid body, and the striated
configuration moreso. No ruptures occur. \\

\noindent
{\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
Taylor-Green flow at low flow rates. For the choices of the flow
strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the
disordered bilayer, $V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$
for the striated configurations. The vesicle stays inact, whereas the
dissordered bilayer is pulled apart. Like in Supplementary Movie S2, the
striated assembly is basically rigid. \\

@@

\noindent
{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
We adopt the relaxed configurations and place the JP structures in the
Taylor-Green flow at higher flow rates. For the choices of the flow
strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the
bilayer, $V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the
striated configurations. Clear structural ruptures occur in each case.
In all cases, there is significant reduction in the orientational order
of the assemblies. While the BC (i) cases are broken into several
pieces, the main body of the BC (ii) and BC (iii) assemblies are not
pulled apart by the background flow.
